### 2020-04-01 draft.tex
added warning

As a corllary, the equivalence $\Dir \simeq \Set^{\downarrow}$ restricts to an
equivalence
$$\Dir_{\ulcorner} \simeq \Set^{\downarrow}_{\ulcorner}$$
between Dirichlet functors and cartesian natural transformations and bundles and
pullback sqaures.
\end{prop}
\begin{proof}
We want to show that for any $f\colon D\to D'$ the square
\begin{equation}\label{eqn.cart1}
\begin{tikzcd}
	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
	D'(1)\ar[d, "\pi'"]\\
	D(0)\ar[r, "f_0"']&
	D'(0)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
\begin{equation}\label{eqn.cart2}
\begin{tikzcd}
  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
  D'(X')\ar[d, "D'(g)"]\\
  D(X)\ar[r, "f_X"']&
  D'(X)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$. We will freely use the natural isomorphism
$D(X)\cong\Set^{\downarrow}(!_X, D!_0)$ from
\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
\ref{eqn.cart2} with
\begin{equation}\label{eqn:cart3}
\begin{tikzcd}
 \Set^{\downarrow}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\downarrow}(!_{X'}, D'!_0)
  \ar[d, "!_{g}^{\ast}"]\\
  \Set^{\downarrow}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
 \Set^{\downarrow}(!_X, D'!_0) 
\end{tikzcd}
\end{equation}

@@

Finally, we calculate $\Ha^{\downarrow}(!_{\ast}, \pi)$ homotopy type-theoretically:
\begin{align*}
\Ha^{\downarrow}(!_{\ast}, \pi) &= \sum_{b : \ast \to B} \sum_{f : X \to E}
                                  (\pi \circ f = b \circ !_X)\\
                                &= \sum_{b : B} \sum_{f : X \to E} \prod_{x : X} (\pi (f x) = b) \\
                                &= \sum_{b : B} \left( X \to \sum_{e : E} (\pi e = b) \right) \\
                                  &\equiv \sum_{b : B}E_b^X.
\end{align*}
\end{proof}

@@

As a corllary, the equivalence $\Dir \simeq \Ha^{\downarrow}$ restricts to an
equivalence
$$\Dir_{\ulcorner} \simeq \Ha^{\downarrow}_{\ulcorner}$$
between Dirichlet functors and cartesian natural transformations and bundles and
pullback sqaures.
\end{prop}
\begin{proof}
TODO
\end{proof}

>>>>

As a corllary, the equivalence $\Dir \simeq \Set^{\downarrow}$ restricts to an
equivalence
$$\Dir_{\ulcorner} \simeq \Set^{\downarrow}_{\ulcorner}$$
between Dirichlet functors and cartesian natural transformations and bundles and
pullback sqaures.
\end{prop}
\begin{proof}
We want to show that for any $f\colon D\to D'$ the square
\begin{equation}\label{eqn.cart1}
\begin{tikzcd}
	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
	D'(1)\ar[d, "\pi'"]\\
	D(0)\ar[r, "f_0"']&
	D'(0)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
\begin{equation}\label{eqn.cart2}
\begin{tikzcd}
  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
  D'(X')\ar[d, "D'(g)"]\\
  D(X)\ar[r, "f_X"']&
  D'(X)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$. We will freely use the natural isomorphism
$D(X)\cong\Set^{\downarrow}(!_X, D!_0)$ from
\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
\ref{eqn.cart2} with
\begin{equation}\label{eqn.cart3}
\begin{tikzcd}
 \Set^{\downarrow}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\downarrow}(!_{X'}, D'!_0)
  \ar[d, "!_{g}^{\ast}"]\\
  \Set^{\downarrow}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
 \Set^{\downarrow}(!_X, D'!_0) 
\end{tikzcd}
\end{equation}

@@

Finally, we calculate $\Ha^{\downarrow}(!_{\ast}, \pi)$ homotopy type-theoretically:
\begin{align*}
\Ha^{\downarrow}(!_{\ast}, \pi) &= \sum_{b : \ast \to B} \sum_{f : X \to E}
                                  (\pi \circ f = b \circ !_X)\\
                                &= \sum_{b : B} \sum_{f : X \to E} \prod_{x : X} (\pi (f x) = b) \\
                                &= \sum_{b : B} \left( X \to \sum_{e : E} (\pi e = b) \right) \\
                                  &\equiv \sum_{b : B}E_b^X.
\end{align*}
{\color{red} But I need a better argument to show that this is a natural
  equivalence of functors --- something involving cartesian fibrations etc etc etc}
\end{proof}

@@

As a corllary, the equivalence $\Dir \simeq \Ha^{\downarrow}$ restricts to an
equivalence
$$\Dir_{\ulcorner} \simeq \Ha^{\downarrow}_{\ulcorner}$$
between Dirichlet functors and cartesian natural transformations and bundles and
pullback sqaures.
\end{prop}
\begin{proof}
We want to show that for any $f\colon D\to D'$ the square
\begin{equation}\label{eqn.type.cart1}
\begin{tikzcd}
	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
	D'(1)\ar[d, "\pi'"]\\
	D(0)\ar[r, "f_0"']&
	D'(0)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
\begin{equation}\label{eqn.type.cart2}
\begin{tikzcd}
  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
  D'(X')\ar[d, "D'(g)"]\\
  D(X)\ar[r, "f_X"']&
  D'(X)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$. We will freely use the natural isomorphism
$D(X)\cong\Set^{\downarrow}(!_X, D!_0)$ from
\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
\ref{eqn.type.cart2} with
\begin{equation}\label{eqn.cart3}
\begin{tikzcd}
 \Set^{\downarrow}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\downarrow}(!_{X'}, D'!_0)
  \ar[d, "!_{g}^{\ast}"]\\
  \Set^{\downarrow}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
 \Set^{\downarrow}(!_X, D'!_0) 
\end{tikzcd}
\end{equation}

The square in Diagram \ref{eqn.type.cart1} is a
special case of that in Diagram \ref{eqn.type.cart2}, namely for $g\coloneqq !_0$;
this establishes the only-if direction.

To complete the proof, suppose that Diagram \ref{eqn.type.cart1} is a pullback, take an arbitrary $g\colon X\to X'$, and suppose given a commutative solid-arrow diagram as shown:
\[
\begin{tikzcd}[sep=small]
  X\ar[rr, "g"]\ar[dd]\ar[rd]&&
  X'\ar[dr]\ar[dd]\ar[dl, dotted]\\&
  D(1)\ar[rr, crossing over]&&
  D'(1)\ar[dd]\\
  1\ar[dr]\ar[rr, equal]&&
  1\ar[dr]\ar[dl, dotted]\\&
  D(0)\ar[from=uu, crossing over]\ar[rr]&&
  D'(0)
\end{tikzcd}
\]
We can interpret the statement that Diagram \ref{eqn.type.cart3} is a pullback as
saying that there are unique dotted arrows making the diagram commute. So, we
need to show that if the front face is a pullback, then there are unique
diagonal dotted arrows as shown in the homotopy type-theoretical sense.
{\color{red} TODO} 
\end{proof}
